FraCaS: Temporal Analysis

### 2020-05-21 paper2020/paper.tex
fix compilation
minor

\usepackage[hyperref]{naaclhlt2019}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\newlist{lingex}{enumerate}{3}
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}

@@

\onelingex{A scandinavian won the nobel prize.\label{ex:onelingex}
\\
{\small\begin{multline*}
\varid{useCl}\, \varid{past}\, \varid{pPos}\\ (\varid{predVP}\, (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{scandinavian\_CN})\\ (\varid{complSlash}\, (\varid{slashV2a}\, \varid{win\_V2})\\ (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{nobel\_prize\_CN})))
\end{multline*}
}}
In our semantics we deal only with present and simple past
tenses. \jp{Is this enough for theory?} Indeed we find that FraCas
does not exercise additional specific tenses (if a more complicated
tense is used, the additional information is also carried by adverbs
or adverbial phrases, in a more specific way.)

>>>>

\usepackage[hyperref]{naaclhlt2019}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}
\newlist{lingex}{enumerate}{3}
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}

@@

\onelingex{A scandinavian won the nobel prize.\label{ex:onelingex}
\\
{\small\begin{multline*}
\varid{useCl}\, \varid{past}\, \varid{pPos}\\ (\varid{predVP}\, (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{scandinavian\_CN})\\ (\varid{complSlash}\, (\varid{slashV2a}\, \varid{win\_V2})\\ (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{nobel\_prize\_CN})))
\end{multline*}
}}
In our semantics we deal only with present and simple past
tenses. \jp{Is this enough for theory?} Indeed we find that FraCas
does not exercise additional specific tenses (if a more complicated
tense is used, the additional information is also carried by adverbs
or adverbial phrases, in a more specific way.) It is not difficult to see how other tenses can be captured under the same general framework.
